### 2020-03-26 CalNotes.tex
some modifications

	\widehat A^\epl(T) \defeq \arg \min_{A \in \R^N} I(X^\epl \mid A) = M^{-1}h,

@@

\corr{
\begin{remark}\label{rem:regularity_diss} In the following, in particular in the proof of Lemma \ref{lem:ergodicity}, we will employ Assumption \ref{as:regularity}\ref{as:regularity_diss} for the whole drift of the SDE \eqref{eq:SDE_MS}, i.e., the function 
	\begin{equation}
		V^\epl(x) \defeq \alpha \cdot V(x) - p\left(\frac{x}{\epl}\right).
	\end{equation}
	Since $p \in L^\infty$, the assumption above is sufficient for $V^\epl$ to satisfy Assumption \ref{as:regularity}\ref{as:regularity_diss} with different values for $a$ and $b$. In particular, if the condition holds for $\alpha \cdot V$ for a given $b > 0$, then one can choose a new value for the same coefficient which is arbitrarily close to the original one for $V^\epl$.
\end{remark}
}

@@

\begin{figure}[t]
	\centering
	\begin{tabular}{c}
		\includegraphics[]{Figures/TrajD1} \\
		\includegraphics[]{Figures/TrajD5} \\
		\includegraphics[]{Figures/TrajD10}
	\end{tabular}
	\caption{\corr{Filtering a trajectory $X^\epl$ obtained with $V(x) = x^2 / 2$, $p(y) = \cos(y)$, $\alpha = 1$, $\sigma = 0.5$ and $\epl = 0.1$. The filtering width is $\delta = \{1, \sqrt{\epl}, \epl\}$ from top to bottom, respectively.}}
	\label{fig:filter}
\end{figure}

@@

Let us from now on consider $\beta = 1$. For this value of $\beta$, the parameter $\delta$ appearing in \eqref{eq:filter} regulates the width of the filtering window. In practice, larger values of $\delta$ will lead to trajectories which are smoother and for which fast-scale oscillations are practically canceled. Let us remark that the filtering width resembles the subsampling step employed for the estimator $\widehat A^\epl_\delta$ introduced and analyzed in \cite{PaS07}. For subsampling, the choice guaranteeing asymptotically unbiased results is $\delta = \epl^\zeta$ with $\zeta \in (0, 1)$, and a similar analysis is due for our filtering technique. For visualization purposes, we depict in Figure \ref{fig:filter} the filtered trajectory $Z^\epl$ for three different values of $\delta$, namely $\delta = \{1, \sqrt{\epl}, \epl\}$. With $\delta = 1$, all oscillations at the fast scale are canceled and the filtered trajectory $Z^\epl$ presents only slow-scale variations are present in $Z^\epl$. Reducing the value of $\delta$, fast-scale oscillations are progressively taken into account.

@@

\begin{example}\label{ex:OrnUhl} A closed form solution of \eqref{eq:FPsystem} can be obtained in a simple homogenized case with the dimension of the parameter $N=1$. Let $p(y) = 0$ and the parameters $\alpha$, $\sigma$ be replaced respectively by $A$ and $\Sigma$. Then, if $V(x) = x^2/2$, equation \eqref{eq:FPsystem} has the analytical solution 
\begin{equation}
\rho^0(x,z) = \frac{1}{C_{\rho^0}} \exp\left(-\frac{A}{\Sigma} \frac{x^2}{2} - \frac{1}{\delta \Sigma} \frac{(x - (1+A \delta)z)^2}{2}\right),
\end{equation}
where
\begin{equation}
C_{\rho^0} = \int_{\R} \int_{\R} \exp\left(-\frac{A}{\Sigma} \frac{x^2}{2} - \frac{1}{\delta \Sigma} \frac{(x - (1+A \delta)z)^2}{2}\right) \dd x \dd z.
\end{equation}
This is the density of a multivariate normal distribution $\mathcal N(0, \Gamma)$, where the covariance matrix is given by
\begin{equation}
\Gamma = \frac{\Sigma}{A (1 + A\delta)} \begin{pmatrix} 1+A\delta & 1 \\ 1 & 1 \end{pmatrix}.
\end{equation}
Let us remark that this distribution can be obtained from direct computations involving Gaussian processes. In particular, it is known that $X \sim \mathcal{GP}(\mu_t, \mathcal C(t, s))$, where at stationarity $\mu_t = 0$ and
\begin{equation}
	\mathcal C(t, s) = \frac{\Sigma}{A} e^{-A|t-s|}.
\end{equation}
The basic properties of Gaussian processes imply that $Z$ is a Gaussian process, and that the couple $(X, Z)^\top$ is a Gaussian process, too, whose mean and covariance are computable explicitly.
\end{example}

@@

\corr{In this section, we analyze the behavior of the filtering-based estimator $\widehat A^\epl_k(T)$ given in \eqref{eq:AHatMixed} when the filtering width $\delta$ is independent of $\epl$. In particular, we suppose there exist positive constants $C_1$ and $C_2$ independent of $\epl$ and $\delta$ such that $C_1 \epl^0 \leq \delta \leq C_2 \epl^0$. In the following, we will write more compactly that $\delta = \mathcal O(\epl^0)$. The analysis in this case is based on the convergence of the couple $(X^\epl, Z^\epl)^\top$ with respect to the multiscale parameter $\epl \to 0$.} In particular, it is known that the invariant measure of $X^\epl$ converges weakly to the invariant measure of $X$ solution of the homogenized equation \eqref{eq:SDE_HOM}. The following result, whose proof is given in Appendix \ref{ap:ProofsErgodic}, guarantees the same kind of convergence for the couple $(X^\epl, Z^\epl)^\top$.

@@

We conclude this section presenting an analogous result to Lemma \ref{lem:FPMarginal} for the limit distribution.

@@

\corr{Let us introduce a notation which will be used throughout the rest of the paper. We denote
\begin{equation}\label{eq:DefCalMTilde}
	\widetilde{\mathcal M}_\epl \defeq \E^{\rho^\epl}[V'(Z^\epl)\otimes V'(X^\epl)], \quad \widetilde{\mathcal M}_0 \defeq \E^{\rho^0}[V'(Z)\otimes V'(X)],
\end{equation}
\i.e., $\widetilde{\mathcal M}_\epl$ is the limit for $T \to \infty$ of the matrix $\widetilde M$ by the ergodic theorem, and $\widetilde{\mathcal M}_0$ is the limit for $\epl \to 0$ of the matrix $\widetilde{\mathcal M}_\epl$ due to Lemma \ref{lem:convMeasure}. For completeness, we introduce here the symmetric matrices $\mathcal M_\epl$ and $\mathcal M_0$ which are defined as
\begin{equation}\label{eq:DefCalM}
	\mathcal M_\epl \defeq \E^{\rho^\epl}[V'(X^\epl)\otimes V'(X^\epl)], \quad \mathcal M_0 \defeq \E^{\rho^0}[V'(X)\otimes V'(X)],
\end{equation}
and which will be employed in the following. We can now introduce the main result, namely the convergence of the filtering-based estimator to the drift coefficient of the homogenized equation.}

@@

\begin{lemma} \label{lem:quadruple_convergence} Let the assumptions of Lemma \ref{lem:quadruple} hold, and let $\delta = \epl^\zeta$ with $\zeta > 0$. Then, it holds
	\begin{equation}
	\lim_{\epl \to 0} \sigma \E^{\eta^\epl} [(1 + \Phi'(Y^\epl))^2V''(Z^\epl) ] = \Sigma \E^{\phi^0} [V''(X)],
	\end{equation}
	where $\Sigma$ is the diffusion coefficient of the homogenized equation \ref{eq:SDE_HOM}.
\end{lemma}

@@

		where $A$ is the drift coefficient of the homogenized equation \eqref{eq:SDE_MS}.

@@

	Therefore, since $\delta = \mathcal O(\epl^\zeta)$ for $\zeta \in (0, 2)$, and due to geometric ergodicity the terms $J_2^\epl(t)$ and $J_3^\epl(t)$ vanish in the limit for $t \to \infty$ and $\epl \to 0$. Furthermore, by Lemma \ref{lem:distanceMandTildeM} and by weak convergence of the invariant measure $\mu^\epl$ to $\mu^0$, we have

@@

There is no guarantee under Assumption \ref{as:regularity} that $\widehat C_{T, \epl}$ is positive define and therefore a covariance matrix. Hence, in this Bayesian setting, we consider a different modification of the likelihood where we perturb only the vector $h$, i.e.,

@@

\begin{theorem}\label{thm:mainTheoremTilde} Let the assumptions of Theorem \ref{thm:mainTheorem} hold. Then, if \corr{$\delta = \epl^\zeta$, with $\zeta \in (0, 2)$}, it holds

@@

	Let us remark that $\widehat A^\epl_k(T)$ has a bounded norm for $\epl$ sufficiently small due to Theorem \ref{thm:mainTheorem}. Now, the triangle inequality yields

@@

	Therefore, due to Theorem \ref{thm:mainTheorem_zeta}, the inequality \eqref{eq:DistATildeAHat} and since $\delta = \mathcal O(\epl^\zeta)$, the desired result holds.

@@

The following lemma characterizes the action of the filter when it is applied to polynomials.
\begin{lemma}\label{lem:FilterPoly} With the notation of Lemma \ref{lem:FilterJensen}, it holds for all $p \geq 0$
	\begin{equation}
		\int_0^t k(t-s)(t-s)^p \dd s \leq C \delta^p,
	\end{equation}
	where $C > 0$ is a positive constant independent of $\delta$.
\end{lemma}
\begin{proof} The change of variable $u = (t-s)/\delta$ yields
	\begin{equation}
		\int_0^t k(t-s)(t-s)^p \dd s = \delta^p \int_0^{t/\delta} u^p e^{-u} \dd u = \delta^p \gamma\left(p+1, \frac{t}{\delta}\right),
	\end{equation}
	where $\gamma$ is the lower incomplete Gamma function, which is bounded by the complete Gamma function $\Gamma(p+1)$ independently of the second argument.
\end{proof}

We can now prove Lemma \ref{prop:zeta}. Denoting $Y_t^\epl \defeq X_t^\epl/\epl$, we will make use of the decomposition
\cite[Formula 5.8]{PaS07}
\begin{equation}\label{eq:App_DiffXtXs}
\begin{aligned}
	X_t^\epl - X_s^\epl &= -\int_s^t (\alpha \cdot V'(X_r^\epl))(1 + \Phi'(Y^\epl_r)) \dd r\\
	&\quad +\sqrt{2\sigma} \int_s^t (1 + \Phi'(Y_r^\epl)) \dd W_r - \epl(\Phi(Y^\epl_t)-\Phi(Y^\epl_s)),
\end{aligned}
\end{equation}
which is obtained applying the Itô formula to $\Phi$, the solution of the cell problem \eqref{eq:CellProblem}.

@@

Corollary \ref{cor:distanceZandX} is a direct consequence of Lemma \ref{prop:zeta} and provides a rough estimate of the difference between the trajectories $X_t^\epl$ and $Z_t^\epl$ when they are at stationarity.

\begin{corollary} \label{cor:distanceZandX} Under Assumption \ref{as:regularity}, let the couple $(X^\epl, Z^\epl)^\top$ be distributed as its invariant measure $\mu^\epl$. Then, if $\delta \leq 1$, it holds for any $p \geq 1$
	\begin{equation}
	\left(\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^p\right)^{1/p} \leq C\left(\epl + \delta^{1/2}\right),
	\end{equation}
	for a constant $C > 0$ independent of $\epl$ and $\delta$.
\end{corollary}
\begin{proof}
	Let $p \geq 1$, then due to Lemma \ref{prop:zeta} there exists a constant $C > 0$ depending only on $p$ such that
	\begin{equation}
	\E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^p \leq C\left(\epl^p + \delta^{p/2}\right).
	\end{equation}
	Let us now remark that this result holds for $X_t^\epl$ being at stationarity and for $Z_t^\epl$ be its filtered process, and not for a couple $(X^\epl, Z^\epl)^\top \sim \mu^\epl$. In order to conclude, we remark that due to Lemma \ref{lem:ergodicity} we have for all $t \geq 0$ and for a constant $C$ depending on the initial condition and $p$  
	\begin{equation}
	\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^p \leq \E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^p + Ce^{-\lambda t},
	\end{equation}
	which, for $t$ sufficiently big, yields the desired result.
\end{proof}

@@

	f(z,b) = \frac12 b^2 V''(z)

@@

	We now consider the remainder and, applying Hölder's inequality, Corollary \ref{cor:distanceZandX}, Lemma \ref{lem:bounded_momentZ} and \eqref{eq:estimate_beta}, we get for $p,q,r$ such that $1/p+1/q+1/r=1$

@@

	Let us introduce the notation 
	\begin{equation}
	\Delta(\epl) = \left| \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] - \Sigma \E^{\phi^0} [V''(X)] \right|,
	\end{equation}
	and note that the aim is to show that $\lim_{\epl \to 0} \Delta(\epl) = 0$. By the triangle inequality we get
	\begin{equation}
	\begin{aligned}
	\Delta(\epl) \le& \left| \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] - \sigma \E^{\eta^\epl} [V''(X^\epl) (1 + \Phi'(Y^\epl))^2] \right| \\
	&+ \left| \sigma \E^{\eta^\epl} [V''(X^\epl) (1 + \Phi'(Y^\epl))^2] - \Sigma \E^{\phi^0} [V''(X)] \right| \\
	\eqdef& \Delta_1(\epl) + \Delta_2(\epl).
	\end{aligned}
	\end{equation}
	We first study $\Delta_1(\epl)$ and due to the boundedness of $\Phi'$, Assumption \ref{as:regularity} and Lemma \ref{cor:distanceZandX} we have
	\begin{equation}
	\Delta_1(\epl) \le C \E^{\eta^\epl} \abs{X^\epl - Z^\epl} \le C (\delta^{1/2} + \epl) = C (\epl^{\zeta/2} + \epl),
	\end{equation}
	which implies
	\begin{equation}
	\lim_{\epl \to 0} \Delta_1(\epl) = 0.
	\end{equation}
	We now consider $\Delta_2(\epl)$. Integrating equation \eqref{eq:FPSDEquadruple} with respect to $z$ and $b$ we obtain the Fokker-Planck equation for the stationary marginal distribution $\lambda \colon \R \times [0,L]$, $\lambda = \lambda(x,y)$, of the couple $(X^\epl,Y^\epl)$
	\begin{equation}
	\begin{aligned}
	\partial_x \left( \left( \alpha \cdot V'(x) + \frac1\epl p'(y) \right) \lambda \right) + \partial_y \left( \left( \frac1\epl \alpha \cdot V'(x) + \frac{1}{\epl^2} p'(y) \right) \lambda \right) & \\
	+ \sigma \left( \partial_{xx}^2 \lambda + \partial_{xy}^2 \left( \frac2\epl \lambda \right) + \partial_{yy}^2 \left( \frac{1}{\epl^2} \lambda \right) \right) &= 0,
	\end{aligned}
	\end{equation}
	whose solution is given by
	\begin{equation}
	\lambda(x,y) = \frac{1}{C_\lambda} \exp \left( - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right),
	\end{equation}
	where
	\begin{equation}
	\begin{aligned}
	C_{\lambda} &= \int_\R \int_0^L \exp \left( - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right) \dd x \dd y \\
	&= \left( \int_\R \exp \left( - \frac\alpha\sigma V(x) \right) \dd x \right) \left( \int_0^L \exp \left( - \frac1\sigma p(y) \right) \dd y \right) \\
	&\eqdef C_{\lambda_x} C_{\lambda_y}.
	\end{aligned}
	\end{equation}
	Therefore, by equations \eqref{eq:SDE_HOM}, \eqref{eq:K_HOM} and \eqref{eq:phi0} we have
	\begin{equation}
	\begin{aligned}
	\sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] &= \sigma \int_\R \int_0^L V''(x) (1 + \Phi'(y))^2 \frac{1}{C_\lambda} \exp \left( - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right) \dd x \dd y \\
	&= \sigma \left( \int_\R V''(x) \frac{1}{C_{\lambda_x}} \exp \left( - \frac\alpha\sigma V(x) \right) \dd x \right) \\
	&\qquad \qquad \times \left( \int_0^L (1+\Phi'(y))^2 \frac{1}{C_{\lambda_y}} \exp \left( - \frac1\sigma p(y) \right) \dd y \right) \\
	&= \sigma K \E^{\phi^0}[V''(X)] = \Sigma \E^{\phi^0}[V''(X)],
	\end{aligned}
	\end{equation}
	which shows that $\Delta_2(\epl) = 0$ and completes the proof. \qed 
\end{appendices}

>>>>

	\widehat A^\epl(T) \defeq \arg \min_{A \in \R^N} I(X^\epl \mid A) = - M^{-1}h,

@@

\corr{
\begin{remark}\label{rem:regularity_diss} In the following, in particular in the proof of Lemma \ref{lem:ergodicity}, we will employ Assumption \ref{as:regularity}\ref{as:regularity_diss} for the whole drift of the SDE \eqref{eq:SDE_MS}, i.e., the function 
	\begin{equation}
		V^\epl(x) \defeq \alpha \cdot V(x) + p\left(\frac{x}{\epl}\right).
	\end{equation}
	Since $p \in L^\infty$, the assumption above is sufficient for $V^\epl$ to satisfy Assumption \ref{as:regularity}\ref{as:regularity_diss} with different values for $a$ and $b$. In particular, if the condition holds for $\alpha \cdot V$ for a given $b > 0$, then one can choose a new value for the same coefficient which is arbitrarily close to the original one for $V^\epl$.
\end{remark}
}

@@

\begin{figure}[t]
	\centering
	\begin{tabular}{c}
		\includegraphics[]{Figures/TrajD1} \\
		\includegraphics[]{Figures/TrajD5} \\
		\includegraphics[]{Figures/TrajD10}
	\end{tabular}
	\caption{\corr{Filtering a trajectory $X^\epl$ obtained with $V(x) = x^2 / 2$, $p(y) = \cos(y)$, $\alpha = 1$, $\sigma = 0.5$ and $\epl = 0.1$. The filtering width is $\delta = \{1, \sqrt{\epl}, \epl\}$ from top to bottom, respectively, and $\beta = 1$.}}
	\label{fig:filter}
\end{figure}

@@

Let us from now on consider $\beta = 1$. For this value of $\beta$, the parameter $\delta$ appearing in \eqref{eq:filter} regulates the width of the filtering window. In practice, larger values of $\delta$ will lead to trajectories which are smoother and for which fast-scale oscillations are practically canceled. Let us remark that the filtering width resembles the subsampling step employed for the estimator $\widehat A^\epl_\delta$ introduced and analyzed in \cite{PaS07}. For subsampling, the choice guaranteeing asymptotically unbiased results is $\delta = \epl^\zeta$ with $\zeta \in (0, 1)$, and a similar analysis is due for our filtering technique. For visualization purposes, we depict in Figure \ref{fig:filter} the filtered trajectory $Z^\epl$ for three different values of $\delta$, namely $\delta = \{1, \sqrt{\epl}, \epl\}$. With $\delta = 1$, all oscillations at the fast scale are canceled and the filtered trajectory $Z^\epl$ presents only slow-scale variations. Reducing the value of $\delta$, fast-scale oscillations are progressively taken into account.

@@

@@

\corr{In this section, we analyze the behavior of the filtering-based estimator $\widehat A^\epl_k(T)$ given in \eqref{eq:AHatMixed} when the filtering width $\delta$ is independent of $\epl$. In particular, we suppose there exist positive constants $C_1$ and $C_2$ independent of $\epl$ and $\delta$ such that $C_1 \epl^0 \leq \delta \leq C_2 \epl^0$. In the following, we will write more compactly that $\delta = \mathcal O(\epl^0)$. The analysis in this case is based on the convergence of the couple $(X^\epl, Z^\epl)^\top$ with respect to the multiscale parameter $\epl \to 0$.} In particular, it is known that the invariant measure of $X^\epl$ converges weakly to the invariant measure of $X$ solution of the homogenized equation \eqref{eq:SDE_HOM}. The following result guarantees the same kind of convergence for the couple $(X^\epl, Z^\epl)^\top$.

@@

\begin{example}\label{ex:OrnUhl} A closed form solution of \eqref{eq:FPsystem_homogenized} can be obtained in the simple case with the dimension of the parameter $N=1$ and $V(x) = x^2/2$. The analytical solution is given by
	\begin{equation}
	\rho^0(x,z) = \frac{1}{C_{\rho^0}} \exp\left(-\frac{A}{\Sigma} \frac{x^2}{2} - \frac{1}{\delta \Sigma} \frac{(x - (1+A \delta)z)^2}{2}\right),
	\end{equation}
	where
	\begin{equation}
	C_{\rho^0} = \int_{\R} \int_{\R} \exp\left(-\frac{A}{\Sigma} \frac{x^2}{2} - \frac{1}{\delta \Sigma} \frac{(x - (1+A \delta)z)^2}{2}\right) \dd x \dd z.
	\end{equation}
	This is the density of a multivariate normal distribution $\mathcal N(0, \Gamma)$, where the covariance matrix is given by
	\begin{equation}
	\Gamma = \frac{\Sigma}{A (1 + A\delta)} \begin{pmatrix} 1+A\delta & 1 \\ 1 & 1 \end{pmatrix}.
	\end{equation}
	Let us remark that this distribution can be obtained from direct computations involving Gaussian processes. In particular, it is known that $X \sim \mathcal{GP}(\mu_t, \mathcal C(t, s))$, where at stationarity $\mu_t = 0$ and
	\begin{equation}
	\mathcal C(t, s) = \frac{\Sigma}{A} e^{-A|t-s|}.
	\end{equation}
	The basic properties of Gaussian processes imply that $Z$ is a Gaussian process, and that the couple $(X, Z)^\top$ is a Gaussian process, too, whose mean and covariance are computable explicitly.
\end{example}

We now present an analogous result to Lemma \ref{lem:FPMarginal} for the limit distribution.

@@

\corr{Let us introduce a notation which will be used throughout the rest of the paper. We denote
\begin{equation}\label{eq:DefCalMTilde}
	\widetilde{\mathcal M}_\epl \defeq \E^{\rho^\epl}[V'(Z^\epl)\otimes V'(X^\epl)], \quad \widetilde{\mathcal M}_0 \defeq \E^{\rho^0}[V'(Z)\otimes V'(X)],
\end{equation}
i.e., $\widetilde{\mathcal M}_\epl$ is the limit for $T \to \infty$ of the matrix $\widetilde M$ by the ergodic theorem, and $\widetilde{\mathcal M}_0$ is the limit for $\epl \to 0$ of the matrix $\widetilde{\mathcal M}_\epl$ due to Lemma \ref{lem:convMeasure}. For completeness, we introduce here the symmetric matrices $\mathcal M_\epl$ and $\mathcal M_0$ which are defined as
\begin{equation}\label{eq:DefCalM}
	\mathcal M_\epl \defeq \E^{\rho^\epl}[V'(X^\epl)\otimes V'(X^\epl)], \quad \mathcal M_0 \defeq \E^{\rho^0}[V'(X)\otimes V'(X)],
\end{equation}
and which will be employed in the following. We can now introduce the main result, namely the convergence of the filtering-based estimator to the drift coefficient of the homogenized equation.}

@@

\begin{lemma} \label{lem:quadruple_convergence} Let the assumptions of Lemma \ref{lem:quadruple} hold, and let $\delta = \epl^\zeta$ with $\zeta > 0$. Then, it holds
	\begin{equation}
	\lim_{\epl \to 0} \sigma \E^{\eta^\epl} [(1 + \Phi'(Y^\epl))^2V''(Z^\epl) ] = \Sigma \E^{\phi^0} [V''(X)],
	\end{equation}
	where $\Sigma$ is the diffusion coefficient of the homogenized equation \eqref{eq:SDE_HOM}.
\end{lemma}

@@

		where $A$ is the drift coefficient of the homogenized equation \eqref{eq:SDE_HOM}.

@@

	Therefore, since $\delta = \mathcal O(\epl^\zeta)$ for $\zeta \in (0, 2)$, the terms $J_2^\epl(t)$ and $J_3^\epl(t)$ vanish in the limit for $t \to \infty$ and $\epl \to 0$. Furthermore, by Lemma \ref{lem:distanceMandTildeM} and by weak convergence of the invariant measure $\mu^\epl$ to $\mu^0$, we have

@@

There is no guarantee under Assumption \ref{as:regularity} that $\widehat C_{T, \epl}$ is positive definite and therefore a covariance matrix. Hence, in this Bayesian setting, we consider a different modification of the likelihood where we perturb only the vector $h$, i.e.,

@@

\begin{theorem}\label{thm:mainTheoremTilde} Let the assumptions of Theorem \ref{thm:mainTheorem_zeta} hold. Then, if \corr{$\delta = \epl^\zeta$, with $\zeta \in (0, 2)$}, it holds

@@

	Let us remark that $\widehat A^\epl_k(T)$ has a bounded norm for $\epl$ sufficiently small due to Theorem \ref{thm:mainTheorem_zeta}. Now, the triangle inequality yields

@@

	Therefore, due to Theorem \ref{thm:mainTheorem_zeta}, the inequality \eqref{eq:DistATildeAHat} and since $\delta = \epl^\zeta$, the desired result holds.

@@

The following lemma characterizes the action of the filter when it is applied to polynomials in $(t-s)$.
\begin{lemma}\label{lem:FilterPoly} With the notation of Lemma \ref{lem:FilterJensen}, it holds for all $p \geq 0$
	\begin{equation}
		\int_0^t k(t-s)(t-s)^p \dd s \leq C \delta^p,
	\end{equation}
	where $C > 0$ is a positive constant independent of $\delta$.
\end{lemma}
\begin{proof} The change of variable $u = (t-s)/\delta$ yields
	\begin{equation}
		\int_0^t k(t-s)(t-s)^p \dd s = \delta^p \int_0^{t/\delta} u^p e^{-u} \dd u = \delta^p \gamma\left(p+1, \frac{t}{\delta}\right),
	\end{equation}
	where $\gamma$ is the lower incomplete Gamma function, which is bounded by the complete Gamma function $\Gamma(p+1)$ independently of the second argument.
\end{proof}

We can now prove Proposition \ref{prop:zeta}. Denoting $Y_t^\epl \defeq X_t^\epl/\epl$, we will make use of the decomposition
\cite[Formula 5.8]{PaS07}
\begin{equation}\label{eq:App_DiffXtXs}
\begin{aligned}
	X_t^\epl - X_s^\epl &= -\int_s^t (\alpha \cdot V'(X_r^\epl))(1 + \Phi'(Y^\epl_r)) \dd r\\
	&\quad +\sqrt{2\sigma} \int_s^t (1 + \Phi'(Y_r^\epl)) \dd W_r - \epl(\Phi(Y^\epl_t)-\Phi(Y^\epl_s)),
\end{aligned}
\end{equation}
which is obtained applying the Itô formula to $\Phi$, the solution of the cell problem \eqref{eq:CellProblem}.

@@

Corollary \ref{cor:distanceZandX} is a direct consequence of Proposition \ref{prop:zeta} and provides a rough estimate of the difference between the trajectories $X_t^\epl$ and $Z_t^\epl$ when they are at stationarity.

\begin{corollary} \label{cor:distanceZandX} Under Assumption \ref{as:regularity}, let the couple $(X^\epl, Z^\epl)^\top$ be distributed as its invariant measure $\mu^\epl$. Then, if $\delta \leq 1$, it holds for any $p \geq 1$
	\begin{equation}
	\left(\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^p\right)^{1/p} \leq C\left(\epl + \delta^{1/2}\right),
	\end{equation}
	for a constant $C > 0$ independent of $\epl$ and $\delta$.
\end{corollary}
\begin{proof}
	Let $p \geq 1$, then due to Proposition \ref{prop:zeta} there exists a constant $C > 0$ depending only on $p$ such that
	\begin{equation}
	\E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^p \leq C\left(\epl^p + \delta^{p/2}\right).
	\end{equation}
	Let us now remark that this result holds for $X_t^\epl$ being at stationarity and for $Z_t^\epl$ be its filtered process, and not for a couple $(X^\epl, Z^\epl)^\top \sim \mu^\epl$. In order to conclude, we remark that due to Lemma \ref{lem:ergodicity} we have for all $t \geq 0$ and for a constant $\widetilde C$ depending on the initial condition and $p$  
	\begin{equation}
	\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^p \leq \E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^p + \widetilde Ce^{-\lambda t},
	\end{equation}
	which, for $t$ sufficiently big, yields the desired result.
\end{proof}

@@

	f(z,b) = \frac12 b^2 V''(z),

@@

	We now consider the remainder and, applying Hölder's inequality, Corollary \ref{cor:distanceZandX}, Lemma \ref{lem:bounded_momentZ}, Assumption \ref{as:regularityZeta} and \eqref{eq:estimate_beta}, we get for $p,q,r$ such that $1/p+1/q+1/r=1$

@@

	Let us introduce the notation 
	\begin{equation}
	\Delta(\epl) = \left| \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] - \Sigma \E^{\phi^0} [V''(X)] \right|,
	\end{equation}
	and note that the aim is to show that $\lim_{\epl \to 0} \Delta(\epl) = 0$. By the triangle inequality we get
	\begin{equation}
	\begin{aligned}
	\Delta(\epl) \le& \left| \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] - \sigma \E^{\eta^\epl} [V''(X^\epl) (1 + \Phi'(Y^\epl))^2] \right| \\
	&+ \left| \sigma \E^{\eta^\epl} [V''(X^\epl) (1 + \Phi'(Y^\epl))^2] - \Sigma \E^{\phi^0} [V''(X)] \right| \\
	\eqdef& \Delta_1(\epl) + \Delta_2(\epl).
	\end{aligned}
	\end{equation}
	We first study $\Delta_1(\epl)$ and due to the boundedness of $\Phi'$, Assumption \ref{as:regularityZeta} and Lemma \ref{cor:distanceZandX} we have
	\begin{equation}
	\Delta_1(\epl) \le C \E^{\eta^\epl} \abs{X^\epl - Z^\epl} \le C (\delta^{1/2} + \epl) = C (\epl^{\zeta/2} + \epl),
	\end{equation}
	which implies
	\begin{equation}
	\lim_{\epl \to 0} \Delta_1(\epl) = 0.
	\end{equation}
	We now consider $\Delta_2(\epl)$. Integrating equation \eqref{eq:FPSDEquadruple} with respect to $z$ and $b$ we obtain the Fokker-Planck equation for the stationary marginal distribution $\lambda \colon \R \times [0,L]$, $\lambda = \lambda(x,y)$, of the couple $(X^\epl,Y^\epl)$
	\begin{equation}
	\begin{aligned}
	\partial_x \left( \left( \alpha \cdot V'(x) + \frac1\epl p'(y) \right) \lambda \right) + \partial_y \left( \left( \frac1\epl \alpha \cdot V'(x) + \frac{1}{\epl^2} p'(y) \right) \lambda \right) & \\
	+ \sigma \left( \partial_{xx}^2 \lambda + \partial_{xy}^2 \left( \frac2\epl \lambda \right) + \partial_{yy}^2 \left( \frac{1}{\epl^2} \lambda \right) \right) &= 0,
	\end{aligned}
	\end{equation}
	whose solution is given by
	\begin{equation}
	\lambda(x,y) = \frac{1}{C_\lambda} \exp \left( - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right),
	\end{equation}
	where
	\begin{equation}
	\begin{aligned}
	C_{\lambda} &= \int_\R \int_0^L \exp \left( - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right) \dd x \dd y \\
	&= \left( \int_\R \exp \left( - \frac\alpha\sigma V(x) \right) \dd x \right) \left( \int_0^L \exp \left( - \frac1\sigma p(y) \right) \dd y \right) \\
	&\eqdef C_{\lambda_x} C_{\lambda_y}.
	\end{aligned}
	\end{equation}
	Therefore, since $\Sigma = K\sigma$ and by equations \eqref{eq:K_HOM} and \eqref{eq:phi0} we have
	\begin{equation}
	\begin{aligned}
	\sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] &= \sigma \int_\R \int_0^L V''(x) (1 + \Phi'(y))^2 \frac{1}{C_\lambda} \exp \left( - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right) \dd x \dd y \\
	&= \sigma \left( \int_\R V''(x) \frac{1}{C_{\lambda_x}} \exp \left( - \frac\alpha\sigma V(x) \right) \dd x \right) \\
	&\qquad \qquad \times \left( \int_0^L (1+\Phi'(y))^2 \frac{1}{C_{\lambda_y}} \exp \left( - \frac1\sigma p(y) \right) \dd y \right) \\
	&= \sigma K \E^{\phi^0}[V''(X)] = \Sigma \E^{\phi^0}[V''(X)],
	\end{aligned}
	\end{equation}
	which shows that $\Delta_2(\epl) = 0$ and completes the proof. \qed 
\end{appendices}
